%Boilerplate LHC is great. the largest discovery machine ever built by humankind.
Experiments at the CERN laboratory in Geneva, studying collisions from the Large Hadron Collider (LHC)~\cite{LHC2008}, have verified the predictive power of the Standard Model (SM) of particle physics. % Characters: LHC or ATLAS Experiment or you and your collaborators? How has this been shown? Establish that this is a thoroughly proven experiment that has already done nobel-prize level work.
% DM is an important problem
Nevertheless, the SM must be incomplete:
It describes all known fundamental particles and their non-gravitational interactions,
but it lacks any particle consistent with the astrophysical evidence for Dark Matter (DM)~\cite{Bertone:2016nfn}.
The \textbf{failure of the SM to account for DM}, which in the universe is five times as abundant as the matter described by the SM, remains one of the most important puzzles in high energy physics research.

% known (not ordinary); by the SM
%  evidenced from astrophysical observations indicates that the SM is an incomplete theory.
% no shortage of ideas, but the puzzle must be resolved with data
% Astrophysical observations indicate that DM is about five times as abundant as ordinary matter in the universe.

Solving this puzzle requires new experimental data. 
Absent clues from particle physics experiments, 
%[AB: rephrase the following] we mainly know what we know about DM characteristics from astrophysics, interacting only gravitationally or with some very feeble interactions with SM matter.
astrophysics observations provide evidence of DM interacting gravitationally, and hints of very feeble interactions between DM and the SM~\cite{Bernal:2017kxu,Steigman:2012nb}. 
%[CD: "probing for" or "probing"?]
%[CD: The sentences below are attempts at conveying complementarity early]
Collider experiments can play a key role in discovering these interactions, complementary to other searches for DM~\cite{Boveia:2018yeb}, since DM could emerge from collisions of SM particles.
Probing for these feeble interactions requires \textbf{large datasets to reveal}.
The LHC will provide larger datasets than any other collider, and detectors such as the ATLAS experiment are well-understood after a decade of peer-reviewed outputs.
Nevertheless, LHC experiments, like many modern experiments, face a data acquisition challenge.
%Original sentence:
%At the same time, the enormous data rates of modern particle physics experiments present a data acquisition challenge.
%With traditional methods, it is not possible to record and store these large datasets when the rare processes are buried in high-rate backgrounds. 
%%Maybe add: the LHC is sensitive to DM if we assume that there are some interactions…
%Other attempts:
%With the largest-ever dataset of proton-proton collisions that could have produced DM particles, 
%At the same time, the enormous data rates of the LHC and of many modern particle physics experiments present a data acquisition challenge.
% if DM interacts with SM particles, these interactions must be very feeble and/or the experimental signals of DM are subtle, requiring large datasets to reveal.
In the dominant approach to data acquisition, the huge datasets produced at the LHC are impossible to fully record and store.
The data needed to discover rare processes may be lost, buried unnoticed in substantially larger backgrounds that are discarded in real-time by a trigger system.
%Maybe add: the LHC is sensitive to DM if we assume that there are some interactions…

As a senior lecturer at Lund University, I will \textbf{lead a research team to search for signs of DM and other new phenomena using new data-taking techniques} for the LHC data to be collected in 2021--2026 by the ATLAS experiment. 
As described in Part B1, the work is divided into five interconnected Work Packages (WPs). %Within this proposal:  
%Earlier text, could restore
%We will deploy a \textbf{new data-taking paradigm} that significantly increases the discovery potential of LHC data for the entire ATLAS experiment, 
%"even though" / "when" is crap 
%even though the LHC center-of-mass energy and dataset size are expected to just be comparable to previous data-taking runs. 
%We will use data collected with new techniques to \textbf{search for signals of broad classes of compelling DM models} and new phenomena that are rare or have so far been neglected, leading to discoveries or constraints with an impact on the global DM community.  
%We will disseminate the results of this research and its innovations through working groups and cross-experimental collaborations of theorists and experimentalists from collider and astrophysics experiments, and to others outside academia. 
%I already said particle physics and astrophysics above
%particle physics and astrophysics. 

In \textbf{WP1} we will extend the capabilities of the ATLAS trigger with comprehensive real-time analysis techniques that significantly increase the discovery potential of the ATLAS experiment. This builds on preliminary work done within my StG to prototype a real-time technique in ATLAS, called Trigger-object Level Analysis (TLA)~\cite{Aaboud:2018fzt}, that has allowed ATLAS to search for new phenomena in orders of magnitude more data than otherwise possible. \\
In \textbf{WP2} we will commission the upgraded ATLAS trigger with early Run-3 data, building on the foundations I developed in Run-2. We will rely on my extensive experience in reconstruction and calibration~\cite{Aad:2014bia,Aaboud:2018kfi} and in measurements and searches during the commissioning phases of every prior LHC run~\cite{Doglioni:2011ema,Aad:2014aqa,ATLAS:2015nsi}. \\ %that I brought to Lund?  
In \textbf{WP3} and \textbf{WP4} we will use the Run-3 datasets recorded with WP1 and WP2 to perform new searches for broad classes of DM models. A first set of searches targets WIMP mediators, probing at electroweak-scale masses with greater sensitivity than existing searches (WP3). A second set targets dark QCD models, making discoveries possible which existing detector reconstruction techniques would miss (WP4). Both sets will exploit my expertise in DM and that of the theoretical particle physics divisions in Lund, as well as my background as one of the founder and co-organizers of the \href{https://lpcc.web.cern.ch/content/lhc-dm-wg-wg-dark-matter-searches-lhc}{LHC Dark Matter Working Group}. \\
In \textbf{WP5} we will disseminate and communicate our results, producing new tools to broaden their usefulness and impact on the global search for DM. I will play coordination roles in, and contribute to, each of several initiatives: a new European DM collaboration between experiment and theory (\href{https://indico.cern.ch/e/idmeu}{iDMEu}), the \href{https://hepsoftwarefoundation.org}{HEP Software Foundation}, and the European Science Cluster of Astronomy and Particle Physics ESFRI research infrastructures project (\href{https://projectescape.eu}{ESCAPE}). 
%ESCAPE: Establish a single collaborative cluster of next generation European Strategy Forum on Research Infrastructures (ESFRI) facilities in the area of astronomy- and accelerator-based particle physics in order to implement a functional link between the concerned ESFRI projects and European Open Science Cloud (EOSC)

This five-year program will advance the state-of-the-art in data-taking and data-processing of enormous datasets at scientific experiments and capture crucial new data on one of the greatest mysteries of our universe. 
